Developing a preprint culture in biology

### 2012-10-17 ms.tex
revtex 4.1 format
Add Liza Gross's suggested reference

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

Open preprint servers offer a great opportunity for open science, especially if
the community embraces the idea of discussing preprints. Initiatives like
Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
new blog discussing arXiv papers in population genetics, will help make arXiv
attractive for scientists looking to promote their work. These initiatives are
important to fully exploit the potential of open preprints servers. Posting
preprints online increases the community of available informal peer reviewers,
and uses the internet for its original community-building purposes.

@@

Another major concern is that if a researcher posts a public preprint that
they will not be allowed to submit their paper to their journal of choice.
This is based on a certain interpretation of the Ingelfinger rule: scientists
should not publish the same manuscript twice \cite{alt96}. A preprint is
simply a document that allows ideas to spread and be discussed, it is not yet
formally validated by the peer-review system. This is why the majority of
publishers do not see arXiv and similar services as a violation of the
Ingelfinger rule, and it is not unseen to have a preprint reproduced almost
exactly in the published version.
%%% TP
%%% Steve Frank papers on ArXiV often end up almost unmodified in JEB
%%% I can dig up the two version so that we can cite them
Almost all of the major publishers in
biology are preprint-friendly, including: Nature Publishing Group, PLOS, BMC,
PNAS, Elsevier, and Springer \ref{table:policies}. The Ecological Society of
America and the Genetics Society of America recently changed their
policies to allow public preprints. In fact,
\emph{Nature} responded to the rumour that they refused manuscripts submitted to
arXiv by saying that ``\emph{Nature} never wishes to stand in the way of
communication between researchers. We seek rather to add value for authors and
the community at large in our peer review, selection and editing'' \cite{nat05}.
Still, a few journals adopt a ``by default'' hostile attitude towards preprints,
mostly due to the lack of clear policy of the publishers, or perhaps because a
preprint culture has not developed in biology and the practice is still
considered unusual. As an example, Wiley-Blackwell, which publishes some of the
leading journals in biology, has no official policy on the matter.

@@

arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
and its use is almost universal in some branches of mathematics and physics.
arXiv provides a reliable citation system for all eprints and is especially
popular in high-energy physics. Physicist Paul Ginsparg created arXiv in 1991
for theoretical high-energy physicists to communicate preprints via email and
ftp, and soon thereafter adopted the newly created world-wide
web\cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
submissions into subcategories of physics, mathematics, computer science,
quantitative biology, finance and statistics.  The quantitative biology category
includes subcategories for Populations and Evolution, Quantitative Methods and
other categories that may be of interest to biologists.

@@

Developing a preprint culture in biology will not solve all problems with the
current publication process. It might however reduce significantly its negative
consequences. Preprint servers speed up publication and make no judgement on
pertinence and originality. Paradoxically, because peer-reviewing is conducted
\emph{after} this step in the process of scientific communication, it might
bring it closer to its fundamental objective. The role of peer-reviewing is to
judge the scientific quality of a study. The peer review process is the first
barrier against the fraudulent and poor quality science susceptible to impede
scientific progress. However, it is now dominated by subjective evaluations,
where trendy contributions are promoted to increase impact factors. Preprints
are by definition not evaluated, neither for their quality nor their pertinence.
Technically, the difference between a preprint and a traditional publication
should be that the latter as the approval stamp by pairs on its quality. The
relevance of a study, its contribution to science, should only be judged
post-publication by many more readers than the typical two-four anonymous
reviewers. With a such a shift in the diffusion strategy, the role of
traditional journals and their editors would be to showcase scientific
discoveries for specialized readership. Such a process should improve even
further their diffusion, not impede it.

@@

We thank Carl Boettiger and Mark Hahnel for helpful comments on an earlier
version of this manuscript.

>>>>

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

Open preprint servers offer a great opportunity for open science, especially if
the community embraces the idea of discussing preprints. Initiatives like
Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
new blog discussing arXiv papers in population genetics, will help make arXiv
attractive for scientists looking to promote their work \cite{lom12}. These initiatives are
important to fully exploit the potential of open preprints servers. Posting
preprints online increases the community of available informal peer reviewers,
and uses the internet for its original community-building purposes.

@@

Another major concern is that if a researcher posts a public preprint that they
will not be allowed to submit their paper to their journal of choice.  This is
based on a certain interpretation of the Ingelfinger rule: scientists should not
publish the same manuscript twice \cite{alt96}. A preprint is simply a document
that allows ideas to spread and be discussed, it is not yet formally validated
by the peer-review system. This is why the majority of publishers do not see
arXiv and similar services as a violation of the Ingelfinger rule. Almost all of
the major publishers in biology are preprint-friendly, including: Nature
Publishing Group, PLOS, BMC, PNAS, Elsevier, and Springer \ref{table:policies}.
The Ecological Society of America and the Genetics Society of America recently
changed their policies to allow public preprints. In fact, \emph{Nature}
responded to the rumour that they refused manuscripts submitted to arXiv by
saying that ``\emph{Nature} never wishes to stand in the way of communication
between researchers. We seek rather to add value for authors and the community
at large in our peer review, selection and editing'' \cite{nat05}.  Still, a few
journals adopt a ``by default'' hostile attitude towards preprints, mostly due
to the lack of clear policy of the publishers, or perhaps because a preprint
culture has not developed in biology and the practice is still considered
unusual. As an example, Wiley-Blackwell, which publishes some of the leading
journals in biology, has no official policy on the matter.

@@

arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
and its use is almost universal in some branches of mathematics and physics.
arXiv provides a reliable citation system for all eprints and is especially
popular in high-energy physics. Physicist Paul Ginsparg created arXiv in 1991
for theoretical high-energy physicists to communicate preprints via email and
ftp, and soon thereafter adopted the newly created world-wide
web \cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
submissions into subcategories of physics, mathematics, computer science,
quantitative biology, finance and statistics.  The quantitative biology category
includes subcategories for Populations and Evolution, Quantitative Methods and
other categories that may be of interest to biologists.

@@

Developing a preprint culture in biology will not solve all problems with the
current publication process. However, It might significantly reduce its negative
consequences. Preprint servers speed up publication and make no judgement on
pertinence and originality. Paradoxically, because peer-reviewing is conducted
\emph{after} this step in the process of scientific communication, it might
bring it closer to its fundamental objective. The role of peer-reviewing is to
judge the scientific quality of a study. The peer review process is the first
barrier against the fraudulent and poor quality science susceptible to impede
scientific progress. Preprints are not filtered, neither for their quality nor
their pertinence.  Technically, the difference between a preprint and a
traditional publication should be that the latter as the approval stamp by pairs
on its quality. The relevance of a study, its contribution to science, should
only be judged post-publication by many more readers than the typical two-four
anonymous reviewers. With a such a shift in the diffusion strategy, the role of
traditional journals and their editors would be to showcase scientific
discoveries for specialized readership. Such a process should improve even
further their diffusion, not impede it.

@@

We thank Carl Boettiger, Mark Hahnel, and Hedvig Nenz\'en for helpful comments on an earlier
version of this manuscript.
